Alleviating the Topology Mismatch Problem in Unstructured and Structured Overlay Networks: A Survey

### 2014-01-21 mard-survey.tex
2012.06.11 (Vassilis) Content revisited. Duplicate text has been removed.

\author{
VASSILIS S. MOUSTAKAS\\\emph{Department of Informatics and Telecommunications}\\\emph{National and Kapodistrian University of Athens}\\
H\"USEYIN AKCAN\\\emph{Department of Software Engineering}\\\emph{Izmir University of Economics}\\
MEMA ROUSSOPOULOS\\\emph{Department of Informatics and Telecommunications}\\\emph{National and Kapodistrian University of Athens}\\
AND\\
ALEX DELIS\\\emph{Department of Informatics and Telecommunications}\\\emph{National and Kapodistrian University of Athens}\\
%  Vassilis Moustakas$^1$, H\"useyin Akcan$^2$, Mema Roussopoulou$^1$ and Alex
%Delis$^1$\\
%  $^1$Department of Informatics and Telecommunications,\\
%  National and Kapodistrian University of Athens\\
%  \mbox{\texttt{\{b.moystakas, mema, ad\}@di.uoa.gr}}\\
%  $^2$Department of Software Engineering,\\
%  Izmir University of Economics, Izmir, Turkey \\
%  \mbox{\texttt{huseyin.akcan@ieu.edu.tr}}
}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% start
%TODO: Maybe this section should be reviewed or deleted or go to another section
%Studying the behaviour of the various peer-to-peer schemes
%\cite{matei_mapgnutella_2002, lv_randomwalks_2002, merugu_str2unstr_2003}
%showed that the ad-hoc network topology of unstructured overlay networks that
%preserve \emph{Power Law} and \emph{Small World} characteristics\footnote{Power
%Law describes the node degree while the Small World describes characteristics
%of path length and clustering coefficient. The clustering coefficient for a
%node $\upsilon$ in a graph $G = \left( V, E \right)$ is defined as the ratio of
%the existing connections between $\upsilon$'s neighbouring nodes to $\gamma
%\times \left( \gamma - 1 \right)$, where $\gamma$ is the number of neighbouring
%nodes of $\upsilon$. High cluster coefficient means that neighbouring nodes of
%any node $\upsilon$ likely connect one another.} \cite{faloutsos_powerlaw_1999,
%saroiu_measurefileshare_2002} offer a more promising approach. Particularly:
%\begin{itemize}
%  \item Peer-to-peer clients are extremely \emph{transient}. Unstructured
%systems can have high maintenance traffic in delivering messages, updating the
%mapping, discovering failures and replicating lost data or pointers, making
%them insufficient on highly volatile networks.
%  \item \emph{Keyword searches} versus \emph{exact-match queries}. In DHTs
%there is a tight control between the data placement and the topology of the
%network. For this reason it is hard to efficiently support partially matched
%queries while Gnutella and other similar systems effortlessly support keyword
%searches and other complex queries since the mechanism is realized locally, on
%a node-by-node basis.
%  \item Popular content is located at multiple peers and thus it is more likely
%for a flooding-based search to return results. DHTs, on the other hand, fit
%better in the systems which require ability to reliably locate content, even in
%the extreme case that only a single-copy exists in the network.
%\end{itemize}
% end
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% TODO: how 
%For this reasons, efforts have been placed for optimizing the efficiency of
%decentralized unstructured peer-to-peer networks. Research mainly focuses on
%\begin{inparaenum}[\itshape i\upshape)]
%  \item reducing unnecessary, redundant communication traffic, and
%  \item exploiting physical locality to reduce communication response.
%\end{inparaenum}
%The goal can be achieved at, both, the application-level network as well as the
%underlying physical one. In the first case by refining the message relay
%techniques, while in the second one, by adaptively reconstructing the
%application network to map as well as possible to the the physical network.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\section{The Topology Mismatch Problem}

%%%%%%%
%%%%%%% TODO: NEEDS REWORDING
%%%%%%% Additional Material
%%%%%%%
%%%%%%%
%%%%%%%
% P4P [16],instead, aimed to provide a general framework for P2P
%applications by developing ISP-application interfaces so that
%application software can use the network layer information,
%such as congestion status and network topology, for better
%performance and resource utilization.

%P4P [37] project attempts to address
%the problem through custom trackers, both for ISPs and P2P
%systems, using an interface based on a primal-dual decomposition
%of an optimization problem. This interface design simplifies
%the realization of traffic-engineering objectives from each parties’
%perspective and ensures the extensibility of the approach. Through
%simulation-based studies and limited experimental deployments,
%these collaborative approaches have been shown to effectively
%reduce network costs while minimally impacting application performance.
%A clear advantage of these proposals is that they
%allow ISPs to incorporate aggregated traffic policies in their tracker
%recommendations (e.g., a particular traffic balance ratio between
%peering providers). However, all of them require deployments
%of oracles for each participating ISP and their effectiveness is
%ultimately predicated on their adoption by P2P applications and a
%trust relationship between P2P users and their ISPs.

% TODO: Taxomize the approaches that have been proposed in the literature
% for unstructured and structured overlay networks
% UNDER CONSTRUCTION
% VERY IMPORTANT SECTION
%\section{Taxonomy}
%
%% TODO: Unstructured
%% UNDER CONSTRUCTION
%Several overlay protocols for dealing with the problems derived from the
%topology mismatch problem have been proposed in the literature. Each
%implementation has different goals but all share some common ground on the
%aspect of the network functionality they focus on, in order to achieve them. In
%this section, the general taxonomy used throughout this paper to categorize the
%algorithms based on their functionality is presented.  The brief description of
%each category and sub-category is stated below.
%
%{\sethlcolor{yellow}\hl{CITE this paper {\cite{liu_ltm_2004}}}}
%
%\subsection{Forwarding based}
%
%Forwarding based methodology is generally adapted by distributed unstructured
%overlay systems. In this approach, a peer selects only a subset of its
%neighbours to re-broadcast query messages. The selection is made using one or a
%combination of various statistical metrics. Examples of such metrics are the
%number of responses received by a neighbour or the connection latency of the
%link between the nodes, etc. The forwarding based approach enhances search
%efficiency but has also several drawbacks. First, the search scope is reduced
%drastically.  Expanding the search scope, on the other hand, is no easy task
%because the overhead of forming multicast trees is proportional to the multicast
%group size.  Second, forwarding based schemes do not consider dynamic joining
%and leaving of peers so they do not scale well on dynamic environments.
%
%\subsection{cache based} 
%
%Caching based protocols are effectively used to reduce traffic costs and
%response times. The caching policy varies depending on the way protocol handles
%the index and the content. Centralized P2P systems use central index servers,
% while local caching systems, such as KazaA, use super peers
%to cache indices in a distributed way. Content caching is also possible in P2P
%systems, where nodes cache the forwarded content for further retrievals.
%Although caching has the above mentioned advantages,  duplication
%of messages still exist, which limits the scalability of these approaches.
%Therefore, cache based approaches are analyzed in the following categories:
%  \begin{itemize}
%    \item \emph{data index caching},
%    \item \emph{content index caching},
%    \item \emph{centralized}, and
%    \item \emph{local}.
%  \end{itemize}
%
%\subsection{overlay optimization based} 
%
%The overlay optimization based protocols modify the topology of the P2P network
%using various techniques. These approaches include creating spanning trees using 
%connection graphs, creating cluster of physically close nodes, or using latency
%information to detect proximity. The brief description of each category is
%presented below:
%
%  \begin{itemize}
%    \item \emph{Spanning tree based}. These approaches construct of a rich graph
%    based on the network connections and build minimum spanning tree on the
%    graphs, causing large traffic overhead to the system
%    \cite{chu_esm_2000,chu_esm_2002}.
%
%    \item \emph{Cluster based}. These approaches select to link physically
%    closer nodes with each other, therefore shrink the search scope
%    significantly while mapping accuracy is not always guaranteed.
%
%    \item \emph{Minimum latency first}. Use of latency as a metric to calculate
%    distance among peers. They require global latency information
%    ``landmarks''\footnote{Measuring latency between peers and stable Internet
%    servers.}.
%
%  \end{itemize}
%
%
%% TODO: Structured
%% UNDER CONSTRUCTION
%\subsection{proximity based}
%Xu \textit{et al.} \cite{xu_globstate_2003} state that there are three ways generating proximity information
%\begin{itemize}
% \item Expanding Ring Search\\
%Expanding ring search can be of two forms. First it can utilize the multicast
%infrastructure in the underlying network in order to emit its messages.
%Unfortunately such infrastructures are not widely deployed thus the
%implementations of this way of generating proximity information is limited to
%blindly flooding the neighbourhood to obtain reasonable results.
%
% \item Heuristics\\
%Heuristics are used in order to reduce the blindness of the expanding ring
%search and make realizations more efficient and effective. Unfortunately a
%common problem of all heuristic approaches is the local minimum pitfall in which
%the search might be caught into.
%
% \item Landmark Binning\\
%Landmark clustering is based on the view that nodes with similar distances to a
%set of predefined well-known landmark nodes are pretty likely of being close to
%each other. But this approach has its weaknesses as well, such as the fact that
%is a rather coarse grained approximation, therefore not particularly well suited
%for differentiating nodes within close distance to each other.
%
%\end{itemize}
%
%Castro \textit{et al.} \cite{castro_proximitydht_2002,castro_topawareroute_2002} on
%the other hand, comment on the three basic approaches in exploiting proximity
%in DHT protocols suggested by Ratnasamy \textit{et al.} \cite{ratnasamy_openq_2002}.
%These are:
%
%\begin{itemize}
% \item Geographic Layout\\
%The node IDs are assigned in such a way that nodes close by in the physical
%network topology, be close in the node ID space as well. Implementations that
%work relatively well with this approach have been incorporated into CAN. Nodes
%measure the RTT between themselves and a set of landmarks in order to match the
%CAN space as much as possible to the physical one. Unfortunately, the approach
%requires well known landmark servers and for that matter is  not fully
%self-organizing which can further lead to imbalanced node distribution. On
%other DHTs, such as Chord or Pastry, another problem emerges.  To gain fault
%tolerant properties, these protocols, replicate key-value pairs on neighbouring
%(in the ID space) nodes. When a proximity-based node ID assignment has been
%used, the needed failure resilience is undermined by the fact that close by
%nodes are more likely to suffer collective failures.
%
% \item Proximity Routing\\
%Proximity routing does not require routing tables be built using any knowledge
%about network proximity. On the other hand it exploits such knowledge in order
%to choose the best next hop during routing a message. This approach 
%balances between choosing the node that will further progress the routing
%towards the destination and choosing the closest entry in the routing table, in
%terms of network proximity. Thus, it is relatively less effective than
%geographical layout when applied to CAN(-like) implementations. Moreover, the
%technique has been incorporated into a version of Chord (TODO: PChord |
%additionally check whether this is true) causing an increase on the overhead of
%node joins and the size as well as maintenance cost of finger tables.
%\cite{dabek_cfs_2001} proposes a server selection scheme for the Chord DHT, on
%the domain of proximity routing selection. In \emph{CFS}, each node predicts
%the entire lookup latency as a function of the total number of nodes and the
%average overlay next routing peer. The problem is that it is very difficult to
%have a clear picture on the total number of nodes and the average hop latency
%from the local. This leads to rough estimations that consequently decreases
%overall performance.
%
% \item Proximity Neighbour Selection\\
%Finally, the third approach, constructs the routing tables using proximity
%knowledge. Tapestry and Pastry's mechanisms of routing table
%maintenance try to minimize the distance to nodes appearing in a peer's routing
%table. Since routing is based on longest node ID prefix match, messages 
%are gradually forwarded to nearby nodes at each routing step.
%\cite{castro_proximityp2p_2002} argues on how Pastry exploits proximity
%neighbour selection in order to create a scheme that is (more) location-aware
%compared to the other well-known DHTs (CAN, Chord).
%
%\end{itemize}
%
%{\sethlcolor{yellow}\hl{
%HA: Possible criteria: based on which protocol (eg Gnutella, CAN etc), peer
%selection (topology selection, cluster, cache etc), supports dynamic update,
%runtimes}}
%%\textbf{Algorithm} & \textbf{Overlay structure} & \textbf{Forwarding} &
%\textbf{Cache} & \textbf{Overlay optimization} & \textbf{Proximity information}
%& \textbf{Base protocol} & \textbf{Dynamic update} & \textbf{Runtime} \\
%
%
%{\sethlcolor{yellow}\hl{
%HA: Possible criteria2: Overlay optimization structure, base protocol (eg
%Gnutella, CAN etc), dynamic update, runtimes, scalability}}
%
%{\sethlcolor{yellow}\hl{
%HA: maybe add also the year of publication, and see if there is a pattern in
%terms of the method and the year??}}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\section{The Algorithms}
%Having understood the nature of the problem that peer-to-peer architecture face, this section starts the discussion of the academic work that has been conducted in the field the last few years. What follows this introduction, does not claim to be a thorough citation of all known protocols that are available out there, but instead, a carefull selection of those that left a distinctive fingerprint contribution in the efforts of the research community to alleviate the topology mismatch problem.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% UNSTRUCTURED
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%\subsection{Narada}
%
%\paragraph*{}
%\emph{End System Multicast} \cite{chu_esm_2000,chu_esm_2001,chu_esm_2002} as well as other  proposes an architecture, where end-systems implement all multicast related functionality (including membership management and packet replication). In \emph{Narada}, the protocol developed in the paper's context, end-systems
%\begin{inparaenum}[\itshape i\upshape)]
%  \item self-organize, in a fully distributed manner,
%  \item into an efficient overlay structure, both from the network and the application perspective,
%  \item with self improving properties,
%  \item adapting to network dynamics\footnote{Long-term variations in Internet path characteristics (i.e. bandwidth, latency e.t.c.)}.
%\end{inparaenum}
%
%\paragraph*{}
%What Narada really does is to construct overlay spanning trees in a two-step process:
%\begin{enumerate}
%  \item It builds a richer connected graph \footnote{ENarada \cite{li_enarada_2008} used Gossip protocol for the construction}, termed a \emph{mesh}, while trying to ensure a couple of desired performance properties:
%    \begin{itemize}
%      \item path quality between any pair of members should be comparable to the quality of the unicast path between them, and
%      \item each member should have a limited number of neighbours on the mesh.
%    \end{itemize}
%
%  \item It computes minimum spanning trees out of the mesh, each rooted at the corresponding source member.
%\end{enumerate}
%
%\paragraph*{}
%Narada incrementally improves the quality of the mesh by adding and dropping overlay links. Members probe each other at random and new links are added depending on what is the gain in doing so. On the other hand, participants, continuously  monitor the utility of existing links, and drop them if they are found to be not usefull.
%
%\paragraph*{}
%Narada protocol achieves relatively good performance for small and medium sized groups involving tens to hundreds of members. This is not, by no means, what a contemporary peer-to-peer system needs to be characterized as scalable, but this work is considered pioneering\footnote{Another similar approach is \emph{Scattercast}\cite{chawathe_scattercast_2000}}, in that it was the first to have conducted a detailed Internet evaluation to analyse and demonstrate the feasibility of an overlay-based, application layer, multicast architecture that can dynamically adapt to bandwidth and latency properties of the physical underlying infrastructure.
%
%\subsection{Gia}
%
%\paragraph*{}
%\emph{Gia} \cite{chawathe_gia_2003} is a decentralized unstructured peer-to-peer file sharing system with the following characteristics:
%\begin{inparaenum}[\itshape i\upshape)]
%  \item replaces Gnutella's flooding with random walks \cite{lv_randomwalks_2002},
%  \item recognizes the importance of overlay network's topology, while using the random walks, and exploits it by incorporating a topology adaptation algorithm,
%  \item introduces a token-based flow control mechanism, and
%  \item detects the significant heterogeneity in peer bandwidth, processing power, disk speed e.t.c. and takes advantage of it.
%\end{inparaenum}
%
%\paragraph*{}
%More specifically, there are four key components in the design of \emph{Gia} which are summarized bellow:
%\begin{enumerate}
%  \item A \emph{dynamic topology adaptation} protocol that puts participating nodes within short reach of high capacity nodes so that these \emph{high-degree} nodes, which due to their high connectivity receive most of the queries, actually have the capacity to handle them.
%  \item An \emph{active flow control} scheme is used to avoid overloaded hot-spots. Heterogeneity is detected and flow control tokens are given to nodes based on the available capacity.
%  \item Every node maintains pointers to to the content that is offered by their immediate neighbours, creating a \emph{one-hop replication} of pointers, scheme.
%  \item A \emph{search protocol} based on random walks, that is biased towards directing queries to high-capacity nodes that are typically best able to answer these queries.
%\end{enumerate}
%
%\subsection{Adaptive Overlay Topology Optimization}
%
%\paragraph*{}
%\emph{Adaptive Overlay Topology Optimization (AOTO)} \cite{liu_auto_2003} is an algorithm for building an overlay multicast tree among each source node and its direct logical neighbours in order to alleviate the mismatching problem while providing a larger query coverage range. It includes the steps of
%\begin{inparaenum}[\itshape i\upshape)]
%  \item \emph{Selective Flooding (SF)}, and
%  \item \emph{Active Topology (AT)}
%\end{inparaenum}
%which are furtherlly discussed in the following paragraphs.
%
%\paragraph*{Selective Flooding (SF)}
%Instead of flooding to all neighbours, SF builds an overlay multicast tree among each peer and its immediate logical neighbours. This reduces overall message burden to the network by making some neighbours non-flooding. The tree is formed using a minimum spanning tree algorithm. For this reason a peer needs to know the costs to all its logical neighbours (e.g. the network delay) as well as between any pair of neighbours. Additional, cost probing, messages need to be added to the original messages defined by the Gnutella protocol.
%
%LTM's SF effectiveness has be proven to be detached from the different physical or overlay topologies. On the other hand, SF is more effective with large number of logical neighbours. It can reach an average optimization rate of 87.4 percent on a logical topology with an average of 30 logical neighbours. 
%
%\paragraph*{Active Topology (AT)}
%At this step the overlay topology is reorganized. Each peer, independently, makes optimizations in the overlay network to alleviate topology mismatching by replacing non-flooding neighbours, with closer nodes. The approach incorporated by the paper is called \emph{Randomized AT} algorithm which picks up a candidate peer at random among the non-flooding neighbour's neighbours. Whenever a new neighbour cost table is received or there is a change of neighbours, the source peer has to re-calculate the multicast tree and apply the randomized AT algorithm.
%
%Different numbers of average logical neighbours has little to do with the effectiveness of AT. If the source has $n$ non-flooding peers, there are $n$ potential neighbour replacements. The overhead to exhaust all $n$ possible replacements can be high, so in practice, after each replacement the source peer can decide whether it needs to find another candidate peer. This is done by computing the cost improvement ratio greater than some predefined termination threshold. The larger the threshold, the slower, in the number of optimization steps, the reduction of the normalized average distance. As a whole the average response time is significantly reduced when more optimization steps taken.
%
%\subsection{Location-aware Topology Matching}
%
%\paragraph*{}
%\emph{Location-aware topology matching} or \emph{LTM} \cite{liu_ltm_2004}, is an algorithm of building an efficient overlay by disconnecting low productive connections and choosing physically closer nodes as logical neighbours while still retaining the search scope and reducing response time of queries. This is done by issuing detector messages by peers, to a small region so that receivers of the detector can record relative delay information and cut inefficient or redundant logical links as well as add closer nodes as direct neighbours. Three operations are defined in LTMband are furtherly discussed in the following paragraphs.
%
%\paragraph*{TTL2-detector flooding}
%\emph{TTL2-detector} messages are designed based on the specification of the Gnutella protocol. Suppose that $d(i, S, v)$ denotes the TTL2-detector which has the message ID of $i$ with TTL value of $v$ and is initiated by $S$. In addition to Gnutella's unified 23-byte header, such a message has a body of two types:
%\begin{itemize}
%  \item short format $d(i, S, 1)$ if $S$ is a direct neighbour of the receiver
%  \item long format $d(i, S, 0)$ if $S$ is within a two-hop distance from the receiver
%\end{itemize}
%This way a peer can calculate link costs from within a one- or two-hop area around it and thus reach peers in $N(S)$ and $N^2(S)$ sets, respectively, in the paper's context. Each peer floods a TTL-detector periodically while it calculates link cost to another peer by receiving other peer's detector messages and checking:
%\begin{itemize}
%  \item the Source Timestamp field and its own clock upon time of receipt for one-hop messages
%  \item the Source Timestamp, TTL1 Timestamp and its own clock upon receipt for two-hop messages
%\end{itemize}
%Of course peer clocks must be synchronized in order to do such checking.
%
%\paragraph*{Low productive connection cutting}
%There are three cases for any peer $P$ who receives $d(i, S, v)$ multiple times:
%\begin{inparaenum}[\itshape i\upshape)]
%  \item $P$ receives both $d(i, S, 1)$ and $d(i, S, 0)$
%  \item $P$ receives multiple $d(i, S, 0)$s from different paths, and P randomly chooses to process one
%  \item $P$ receives one $d(i, S, 1)$ and multiple $d(i, S, 0)$s, and $P$ processes $d(i, S, 1)$ and one randomly selected $d(i, S, 0)$
%\end{inparaenum}
%If the link with the largest cost is found and is a direct neighbour then the connection is put in a will-cut list and stays there for a certain period of time. If it is not, then it is handled by other peers. After that period, connections are cut and recorded to $P$'s cut-list.
%
%\paragraph*{Source probing}
%For a peer $P\in(N^2(S) - N(S))$ who receives only one $d(i, S, 0)$, the cost of $PS$ is obtained (with list look-up or probing). Then $P$ compares it with the cost from each hop and if $PS$ has the largest cost, $P$ will not keep this connection, while otherwise the connection will be created.
%
%\paragraph{}
%Supposing $n$ is the number of peers, $c_n$ is the average number of neighbours and $c_e$ is the average cost of logical links, then in the flooding-based search the traffic incurred by one query from an arbitrary peer in a peer-to-peer network is $O(n)$. As observed in the Gnutella network \cite{sripanidkulchai_gnutella_2001}, each peer issues $0.3$ queries per minute in average, thus the per minute traffic incurred by the network with $n$ peers is $O(n^2)$. Because each $d(i, S, v)$ has a TTL of $2$ in each source peer, the traffic for one time LTM optimization in all peers is at most $2nc_n^2c_e$. If each peer uses LTM $k$ times per minute, the total traffic incurred is $2knc_n^2c_e$. Simulation shows the best value for $k$ is $2$ or $3$. So, the traffic overhead caused by LTM to the network is $O(n)$.
%
%TTLj-detectors, with $j > 2$, would detect and break cycles with more than 4 links. LTM though, does not use such detectors because detector-flood traffic would increase significantly, and cut links between two end-peers, could cause queries initiated by them to traverse a path much more expensive than the cost on the the cut link.
%
%\paragraph{}
%LTM disadvantages are
%\begin{inparaenum}[\itshape i\upshape)]
%  \item disagreement of measured delay due to unsynchronized clocks causes problems when deciding the cut positions, which can influence the network connectivity, and
%  \item the network delay metric mainly focuses on disabling the connections between peers physically far away without considering the shortcuts created by powerful peers.
%\end{inparaenum}
%
%\begin{figure}
%\centering
%  \includegraphics[scale=0.4]{img/ltm_multid.jpeg}
%\caption{Peer $P$ receives $d(i, S, v)$ multiple times}
%\label{figure:ltm_multid}
%\end{figure}
%
%\begin{figure}
%\centering
%  \includegraphics[scale=0.4]{img/ltm_example.jpeg}
%\caption{A full example of LTM}
%\label{figure:ltm_example}
%\end{figure}
%
%\subsection{Scalable Bipartite Overlay}
%\emph{Scalable Bipartite Overlay (SBO)} \cite{liu_bipartite_2007} employs an efficient strategy to select query forwarding paths and logical neighbours. The topology construction and optimization of SBO consist of four phases:
%\begin{enumerate}[\itshape i\upshape)]
%  \item When a new peer is joining the network, it will randomly take an initial colour; say red or white. This colour is not to be changed for the time the peer stays connected. If it leaves and then rejoins it will, again, have to pick a colour, randomly. Thus all peers are separated into two groups, red or white. Then the bootstrap host will provide, the joining peer, with a list of active peers, including their colour information, in order for the later to establish connections to different colour peers. This way, all peers form a bipartite overlay.
%  \item White peers probe distances with their immediate (red) neighbours, form a cost table and send this table to their corresponding red neighbours.
%  \item Each red peer builds a minimum spanning tree using the obtained neighbour cost tables. These are two-hop diameter trees so white peers do not need to build one. The links that are part of a minimum spanning tree are called \emph{forwarding connections (FC)} while the rest \emph{non-forwarding (NFC)}.
%  \item Having a minimum spanning tree with two hops a red peer is able to send its queries within that range. Some white peers, though, have become non-forwarding neighbours. In this phase, such a (white) neighbour will try to find another red peer being two hops away from its current red neighbour to replace the later as its new neighbour.
%\end{enumerate}
%
%\begin{figure}
%\centering
%  \includegraphics[scale=0.4]{img/sbo_efficient_forward.jpeg}
%\caption{A red peer $P$ has a small overlay topology of $N(P)$ and $N^2(P)$ and computes the efficient forwarding paths}
%\label{figure:sbo_efficient_forward}
%\end{figure}
%
%\begin{figure}
%\centering
%  \includegraphics[scale=0.4]{img/sbo_neighbour_replace.jpeg}
%\caption{Neighbor replacement}
%\label{figure:sbo_neighbour_replace}
%\end{figure}
%
%In a static enviromnent LTM may reduce traffic cost by around 80 to 85 percent while SBO reduces traffic cost between 85 and 90 percent. However, LTM  is proved to converge in around 2-3 steps while SBO needs 4-5 steps. Moreover LTM reduces response time by more than 60 percent in 3 steps while SBO needs 8. In a dynamic environment (10 minute average peer lifetime, 0.3 queries/sec by each peer) SBO and LTM reduce the average traffic cost per query (including the overhead due to the optimization steps) by 85 and 80 percent, respectively. Moreover LTM reduces the response time per query to 30 percent while SBO to 35 percent.
%
%\subsection{Adaptive Connection Establishment}
%
%\paragraph{}
%\emph{Adaptive Connection Establishment (ACE)} \cite{liu_ace_2004} builds an overlay multicast tree among each source node and the peers within a certain diameter from the source peer and optimizes the neighbour connections that are not in that tree.
%
%\paragraph{}
%ACE indicates three phases for its algorithm:
%\begin{enumerate}[\itshape i\upshape)]
%  \item Calculate cost between nodes using network delay as a metric. Each peer probes the costs with its immediate logical neighbours and forms a \emph{neighbour cost table (NCT)} using a special routing message type. Two neighbouring peers exchange their NCTs in order for every peer to obtain the cost between any pair of its local neighbours forming a small overlay topology.
%  \item Based on obtained NCTs a minimum spanning tree among each peer and its immediate neighbours is built (Figure~\ref{figure:ace_phase2}).
%  \item Physically far away neighbours are replaced by physically close neighbours. In ACE a peer, say $S$, probes the distance between one of its non-flooding neighbour's neighbour, say $G$ and $H$ respectively. If the link to neighbour's neighbour is smaller than that to the neighbour, the later is cut. If this is not the case but $S$ finds that cost of $GH$ is even larger than that of the $SH$, $S$ will keep $H$ as a new neighbour. Obviously, if $SH$ is larger than $SG$ and $GH$, the connection will not be established and $S$ will continue probing another neighbour's neighbour. The algorithm described is conducted within $1$-neighbour closure (among its source peer and all its direct neighbours) but the optimization scope can be enlarged. The larger the scope, the better topology matching improvement but also the greater the computational overhead (Figure~\ref{figure:ace_phase3}).
%\end{enumerate}
%
%\paragraph{}
%Simulations in \cite{liu_acesims_2004} show that the average scope of each query to cover the same scope of nodes is reduced by about 65 percent without losing any autonomy feature, while the average response time can be reduced by 35 percent. Larger diameter topologies lead to better topology optimization rate but also to higher communication and computation overhead. It was also found that it is more effective in higher connectivity dense topologies. Compared to LTM, it comes short of convergence speed. In \cite{ni_mismatch_2004} shows reduction of both total traffic (90 percent) and response time (80 percent) to message queries without shrinking the search scope. SBO, on the other hand, achieves approximately 85 percent reduction on traffic cost and about 60 percent reduction on query response time. Last but not least, it is concluded that work must be done on incorporating a more sophisticated selection policy for candidate non-flooding peers.
%
%\begin{figure}
%\centering
%  \includegraphics[scale=0.4]{img/ace_phase2.jpeg}
%\caption{Second phase in ACE}
%\label{figure:ace_phase2}
%\end{figure}
%
%\begin{figure}
%\centering
%  \includegraphics[scale=0.4]{img/ace_phase3.jpeg}
%\caption{Third phase in ACE}
%\label{figure:ace_phase3}
%\end{figure}
%
%\subsection{Hops Adaptive Neighbour Discovery}
%
%\paragraph{}
%Paper \cite{chen_hand_2006} proposes a new algorithm named \emph{Hops Adaptive Neighbour Discovery (HAND)} which uses a fully distributed triple hop adjustment strategy to address the topology mismatch problem. The advantages of the algorithm compared to other approaches are that
%\begin{inparaenum}[\itshape i\upshape)]
%  \item it does not need any clock synchronization,
%  \item it is a fully distributed algorithm making it robust and reliable in decentralized systems,
%  \item the traffic overhead of the triple hop adjustment is very low,
%  \item it is applicable to dynamic peer-to-peer environments, and
%  \item maintains lower query response time.
%\end{inparaenum}
%
%\paragraph{}
%The algorithm's ultimate goal is the optimal overlay, the \emph{Logical Communication Network (LCN)} in the paper's context. The key concept of the algorithm is that a graph $G^{*}$ that describes an LCN and a graph $G$ that describes the current overlay are matched only if all peer hop sequences $(v_1, v_2, \ldots, v_k)$ in $G$ exist in $G^{*}$ and in the same order. In practice triple sequences $(v_1, v_2, v_3)$ are used.
%
%\paragraph{}
%The mismatching detection is done in the following way. Suppose we want to verify peer sequence $v_2-v_1-v_3$ (see Figure~\ref{figure:hand_com_overlay}). A pair of probing messages are sent from $v_1$ to $v_2$ and $v_3$. Suppose delays of $(v_1,v_2)$ and $(v_1,v_3)$ are are denoted as $x$ and $z$, respectively. When the probing message arrives to $v_2$ it forwards it directly to $v_3$. Similarly, when the probing message arrives to $v_3$, it forwards it directly to $v_2$. These last steps are performed in order to obtain delays of $(v_2,v_3)$ and $(v_3,v_2)$ physical paths, respectively, denoted by $y$.
%\begin{itemize}
%  \item If $y=z-x\pm\varepsilon$, sequence $v_2-v_1-v_3$ is mismatched and should be adjusted to $v_1-v_2-v_3$ by deleting edge $(v_1,v_3)$ and adding a new $(v_2,v_3)$ (see Figure~\ref{figure:hand_matchtriple_lemma3}).
%  \item if $y=x-z\pm\varepsilon$, sequence $v_2-v_1-v_3$ is mismatched and should be adjusted to $v_1-v_3-v_2$ by deleting edge $(v_1,v_2)$ and adding a new $(v_3,v_2)$ (see Figure~\ref{figure:hand_matchtriple_lemma4}).
%\end{itemize}
%$\varepsilon$ is a small positive real number denoting additional delays caused by possible forwarding and jitter delays.
%
%\begin{figure}
%\centering
%  \includegraphics[scale=0.4]{img/hand_com_overlay.jpeg}

>>>>

\author{
VASSILIS S. MOUSTAKAS\\
\texttt{b.moystakas@di.uoa.gr}\\
\emph{Department of Informatics and Telecommunications}\\
\emph{National and Kapodistrian University of Athens}\\
H\"USEYIN AKCAN\\
\texttt{huseyin.akcan@ieu.edu.tr}\\
\emph{Department of Software Engineering}\\
\emph{Izmir University of Economics}\\
MEMA ROUSSOPOULOS\\
\texttt{mema@di.uoa.gr}\\
\emph{Department of Informatics and Telecommunications}\\
\emph{National and Kapodistrian University of Athens}\\
AND\\
ALEX DELIS\\
\texttt{ad@di.uoa.gr}\\
\emph{Department of Informatics and Telecommunications}\\
\emph{National and Kapodistrian University of Athens}
}

@@

% \item Proximity Neighbour Selection\\
%Finally, the third approach, constructs the routing tables using proximity
%knowledge. Tapestry and Pastry's mechanisms of routing table
%maintenance try to minimize the distance to nodes appearing in a peer's routing
%table. Since routing is based on longest node ID prefix match, messages 
%are gradually forwarded to nearby nodes at each routing step.
%\cite{castro_proximityp2p_2002} argues on how Pastry exploits proximity
%neighbour selection in order to create a scheme that is (more) location-aware
%compared to the other well-known DHTs (CAN, Chord).
%
%\end{itemize}
%
%{\sethlcolor{yellow}\hl{
%HA: Possible criteria: based on which protocol (eg Gnutella, CAN etc), peer
%selection (topology selection, cluster, cache etc), supports dynamic update,
%runtimes}}
%%\textbf{Algorithm} & \textbf{Overlay structure} & \textbf{Forwarding} &
%\textbf{Cache} & \textbf{Overlay optimization} & \textbf{Proximity information}
%& \textbf{Base protocol} & \textbf{Dynamic update} & \textbf{Runtime} \\
%
%
%{\sethlcolor{yellow}\hl{
%HA: Possible criteria2: Overlay optimization structure, base protocol (eg
%Gnutella, CAN etc), dynamic update, runtimes, scalability}}
%
%{\sethlcolor{yellow}\hl{
%HA: maybe add also the year of publication, and see if there is a pattern in
%terms of the method and the year??}}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% TODO: SOME INFORMATION ON ISP-ASSISTED TOPOLOGY AWARENESS
%       ATTENTION: NEEDS REWORDING
%
% P4P [16],instead, aimed to provide a general framework for P2P
%applications by developing ISP-application interfaces so that
%application software can use the network layer information,
%such as congestion status and network topology, for better
%performance and resource utilization.

%P4P [37] project attempts to address
%the problem through custom trackers, both for ISPs and P2P
%systems, using an interface based on a primal-dual decomposition
%of an optimization problem. This interface design simplifies
%the realization of traffic-engineering objectives from each parties’
%perspective and ensures the extensibility of the approach. Through
%simulation-based studies and limited experimental deployments,
%these collaborative approaches have been shown to effectively
%reduce network costs while minimally impacting application performance.
%A clear advantage of these proposals is that they
%allow ISPs to incorporate aggregated traffic policies in their tracker
%recommendations (e.g., a particular traffic balance ratio between
%peering providers). However, all of them require deployments
%of oracles for each participating ISP and their effectiveness is
%ultimately predicated on their adoption by P2P applications and a
%trust relationship between P2P users and their ISPs.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
